### 2018-03-20 papers.tex
papers.tex: Adjust per-paper page number overrides for the new formatting

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\ainput{mftpc/trail-intro} % Before Stefan and Ben's paper
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2cm}
	{}
\ainput{mftpc/itg-miss}

>>>>

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\ainput{mftpc/trail-intro} % Before Stefan and Ben's paper
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2.5cm}
	{}
\ainput{mftpc/itg-miss}
